Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2018-12-09 article_springer/article_springer.Rmd
revert CTRE plot

times <- cumsum(stabledist::rstable(n, tail, 1, sigma, pm=1))
#times<-cumsum(rpareto(n,tail))
magnitudes <- extRemes::revd(n, scale = 1, shape = 0)
sim_ctre <- ctre(data.frame(times, magnitudes)) 
par(mfrow = c(1,2)) 
p1<-plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
p2<-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
```

>>>>

times <- cumsum(stabledist::rstable(n, tail, 1, sigma, pm=1))
#times<-cumsum(rpareto(n,tail))
magnitudes <- extRemes::revd(n, scale = 1, shape = 0)
sim_ctre <- ctre(data.frame(times, magnitudes)) 
par(mfrow = c(1,2)) 
p1<-plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
p2<-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data")
library(gridExtra)
grid.arrange(p1, p2, nrow = 2)
```
